---
title: "R Notebook"
output: html_notebook
---
# Calling relevant libraries
```{r}
library(tidyverse)
library(here)
library(janitor)
```

#READING THE DATA-SET
```{r}
candy_data <- read_csv(here("clean_data/candy_all_years_clean.csv"),
                       col_types = cols(
                            gender = col_character(),
                            country = col_character()
                            ))
```



Analysis questions

1> What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

```{r}
candy_data %>%
  filter(!is.na(rating)) %>%
   summarise(total_no_of_candy_ratings = n())

View(candy_data %>%
  filter(rating == "JOY" | rating == "DISPARE" | rating == "MEH")) %>%
  summarise(total_no_of_candy_ratings = n())
```
2> What was the average age of people who are going out trick or treating and the average age of people 3. not going trick or treating?

```{r}
candy_data %>%
  group_by(trick_or_treat_yourself) %>%
  summarise( average_age = mean(age,na.rm = TRUE))
```

3> For each of joy, despair and meh, which candy bar revived the most of these ratings?
```{r}
candy_data %>%
  filter(!is.na(rating))%>%
  group_by(rating, candy_name) %>%
  summarise( count = n()) %>%
  filter(count == max(count))
```

4> How many people rated Starburst as despair?
```{r}
candy_data %>%
  filter(candy_name == "starburst", rating == "DESPAIR") %>%
  summarise (total_starburst_despair = n())
```

For the next three questions, count despair as -1, joy as +1 and meh as 0.

5> What was the most popular candy bar by this rating system for each gender in the dataset?

# First lets create a seperate column called emotion_numeric using the recode function
```{r}
candy_data_numeric  <- candy_data %>%
  mutate(rating_numeric = recode(rating, DESPAIR = -1, JOY = 1, MEH = 0))
```


```{r}
candy_data_numeric %>%
  group_by(gender, candy_name)%>%
  summarise(sum = sum(rating_numeric, na.rm = TRUE)) %>%
  filter(sum == max(sum))
```

6> What was the most popular candy bar in each year?

```{r}
candy_data_numeric %>%
  group_by(year, candy_name)%>%
  summarise(sum = sum(rating_numeric, na.rm = TRUE)) %>%
  filter( sum == max(sum))
```

7> What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?

```{r}
candy_data_numeric%>%
  mutate(country = if_else(country %in% c("united states", "canada", "united kingdom"), country, "other")) %>%
  group_by(country, candy_name)%>%
  summarise(sum = sum(rating_numeric, na.rm = TRUE)) %>%
  filter( sum == max(sum))
```

